---
title: "assessment1.2"
author: "Kevin Lukose 4629418"
date: "22/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- The title of your document should be Assessment 1.2
- The Author is your name and student id
- The date is the date you created he document

You will need to answer each task using the text/graph narration and include R chunks to show how you get them.

2. Create the heading of the first level and call it Data wrangling

3. Insert an R chunk and create a variable with this dataset
https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv

The name of the variable should be `fastfood`

Display the types of variables in the dataset using `skimr` package

4. Show the number of observations for each restaurant.

5. Calculate and display the average number of calories for each restaurant.

6. Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories` 

7. Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. **

8. Display the count of observations per each type of restaurant

9. Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat` 

10. Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 

- Save your .rmd file 

- Do a commit in Git tab

- Push in the same tab

# Data Wrangling

```{r, echo=TRUE}
library(tidyverse)
library(skimr)

fastfood <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

head(fastfood)

skim(fastfood)

fastfood1 <- fastfood %>% group_by(restaurant) %>% summarise(`nofobservations`=n())

fastfood %>% group_by(restaurant) %>% summarise(`average`=mean(calories))

fastfood %>% group_by(restaurant) %>% summarise(`average_calories`=mean(calories))

fastfood2 <- fastfood %>% group_by(restaurant) %>% summarise(`total fat`= sum(total_fat))
#Data visualization helps to tell stories by curating data into a form easier to understand, highlighting the trends and outliers. A good visualization tells a story, removing the noise from data and highlighting the useful information

ggplot(data=fastfood2, aes(x=restaurant, y= `total fat`)) + geom_bar(stat="identity")

ggplot(data=fastfood1, aes(x=restaurant, y= `nofobservations`)) + geom_bar(stat="identity")

fastfood %>% group_by(restaurant) %>% summarise(`max fat`=max(total_fat))

fastfood3 <- fastfood %>% filter(restaurant == "Mcdonalds")
fastfood3

ggplot(data=fastfood3, aes(x=protein, y=sugar)) + geom_point(stat= "identity")
```




